Hybrid Threads \\ for the \\ Parrot Virtual Machine

### 2012-06-25 Paper.tex
Line breaks in title
Examples for chapter 2

\title{Hybrid Threads for the Parrot Virtual Machine}

@@

@@

>>>>

\title{Hybrid Threads \\ for the \\ Parrot Virtual Machine}

@@

Following is an example of a multithreaded program in Java. The program spawns 10,000 threads, each one waiting for the \textit{starter} variable to be set to 1 before adding it's name to an array:
\input{thread-java}

The program exploits the fact that all methods in the \textit{Vector} class are synchronized, i.e. thread-safe. If the \textit{results} array was a non-thread-safe \textit{ArrayList} instead, access would have to be locked manually:

\begin{JavaCode}
synchronize(results) {
    results.add(name);
}
\end{JavaCode}

@@

Following is an example of a multithreaded program in Python. The program spawns 10,000 threads, each one waiting for the \textit{starter} variable to be set to 1 before appending it's name to an array:
\input{thread-python}

Even though many threads append to the same array, they do not have to take any locks. The GIL implicitly protects the array by allowing only one Python instruction to be run at any time.
